---
title       : Alex's Super Duper Shiny App
subtitle    : Predicting The Duration of Old Faithful Eruptions Based on Waiting Time
author      : Alex Cook
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [quiz, bootstrap, mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
logo        : alex photo.jpg
---

## What is it

Have you ever found yourself waiting at Old Faithful, trying to figure out for how long it was going to erupt?  

The wait is over! Alex's new Super Duper Shiny App uses loads of data on Old Faithful to predict how long the next
eruption will be.

The app is located at:
https://alexbcook.shinyapps.io/oldfaithful/

--- .class #id 

## The Model

The predictions are based on an extremely simple dataset containing data only on eruption duration and wait times between eruptions. A simple univariate regression model of the form

$EruptionDuration = \beta_0 + \beta_1 * WaitingTime + \epsilon$

```{r, echo=F, results='hide'}
library(stats)
data(faithful)
mod<-lm(eruptions~waiting,data=faithful)
beta0<-round(summary(mod)$coef[1],2)
beta1<-round(summary(mod)$coef[2],3)
```

was performed on the dataset, with the resulting intercept of `r beta0` and a coefficient on waiting time of `r beta1`.

---

## Plotting the relationship
Here is a simple plot of the relationship between eruption time and waiting time, with the regression line overlaid, as well as the code for generating it:
```{r}
plot(faithful$waiting,faithful$eruptions,pch=19,col="blue",xlab="Waiting",ylab="Duration")
lines(faithful$waiting,mod$fitted,lwd=3)
```

--- &radio

## Quiz

To prove that you've actually gone to my shinyapps.io site and tested my app, what is the predicted eruption time if 
the eruption started after you've been waiting for 2hrs, 35 minutes?

1. 15.9
2.  _9.85_
3. 10.0
4. 4.56

***.hint 
Go to https://alexbcook.shinyapps.io/oldfaithful/, enter 155 and hit Submit.
***.explanation 
It's 9.85 minutes.

